
\begin{singlespace}
{\setlength{\parindent}{0pt}
\DefineShortVerb[commandchars=\\\{\}]{\`}
{\large \textbf{Usage:}}

Download the repository by using git

`git clone git://github.com/bryanwweber/pysens.git`

No other compilation is necessary. Python 3 is required.
The runtime behavior of the script is configured by setting options in
the `pysens.conf` file. A sample `pysens.conf` is included in the
distribution and reproduced below.

The script can be run on Linux either by setting the executable bit
and executing the program from the shell e.g.\\
`./run_sens.py`\\
or by calling\\
`python3 run_sens.py`.\\
On Windows, it should be run by\\
`py run_sens.py`\\
Note: I haven't tested this on Windows

\blankline

{\large `pysens.conf` \textbf{options:}}

The `pysens.conf` file must either have `[DEFAULT]` on the first line,
or one of the following options. No other text is supported on the first
line. If options are given that aren't specified below, they will be
ignored.

The options can be specified by:

`option = value or option : value`

The following options are available:

\begin{Verbatim}
reactions - The set of reactions to be analyzed. Can be one of:

all - use all of the reactions in the mechanism
comma-separated list (e.g. 1,2,3) - use the specified reactions
colon-separated values - specify a range of reactions
                         with either start:stop or
                         start:interval:stop syntax.
                         If stop is not given, it
                         defaults to the number of
                         reactions in the mechanism.
                         Thus, all and 1: are
                         equivalent. end is a
                         synonym for the number
                         of reactions. E.g. 1:10 or
                         1:2:10 or 1:2: or 1:2:end

mech input file - The mechanism to be analyzed.

thermo input file - Optional if the thermo information
                    is specified in the mech input file.

outputfile - The base name of the output file. The full
             output file name will be set by concatenating
             outputfile + rfactor + sim input file.

factors - The multiplication factors to be considered.
          Multiple multiplication factors should be
          separated by commas.

sim input files - Valid CHEMKIN-Pro input files for the
                  test cases desired.

chemkin root - The root directory of the CHEMKIN-Pro
               install. Accepts shell variables, including
               those set by the CHEMKIN setup script
               that should run at logon.
\end{Verbatim}

{\large \textbf{Sample} `pysens.conf` \textbf{file:}}
\VerbatimInput{includes/pysens.conf}

The following is the code that makes up this script.

\cleardoublepage

{\Large `run\_sens.py`, the main driver script}
\input{includes/run_sens}

\cleardoublepage

{\Large `mechinterp.py`, containing the mechanism interpreter}
\input{includes/mechinterp}

\cleardoublepage

{\Large `sens\_helper.py`, containing helper functions}
\input{includes/sens_helper}
}
\end{singlespace}
